A Methodology and Implementation of Automated Emissions Harmonization for Use in Integrated Assessment Models

### 2018-01-29 paper.tex
saving to make multifigure

The remainder of this paper describes the methodology and implementation of the
harmonization software \code{aneris} \cite{matthew_gidden_2017_802832}, written
in the Python programming language (detailed documentation available
\href{http://mattgidden.com/aneris/}{online}). Section \ref{sec:meths} provides
a detailed description of the underlying mathematical components of
\code{aneris} as well as the procedural workflow. The results of applying the
automated harmonization mechanism on two example IAM scenarios, one with
emissions growth and another with emissions mitigation, is presented in Section
\ref{sec:results}. Finally, the general effectiveness and potential future
improvements on the automated methodology is discussed in Section
\ref{sec:future}.
\section{Methodology \& Implementation}\label{sec:meths}

@@

\subsection{\code{aneris} Workflow}\label{sec:workflow}

The full \code{aneris} workflow is comprised of a number of components shown
graphically in Figure \ref{fig:workflow}. Unharmonized model data and a
run-control configuration are read in via an Excel spreadsheet. Data is assumed
to be in the IAMC format, i.e., using \code{Model}, \code{Scenario},
\code{Region}, \code{Variable}, and \code{Unit} columns in addition to columns
representing each modeled time period.

@@

>>>>

The remainder of this paper describes the methodology and implementation of the
harmonization software \code{aneris} \cite{matthew_gidden_2017_802832}, written
in the Python programming language (detailed documentation available
\href{http://mattgidden.com/aneris/}{online}). Section \ref{sec:meths} provides
a detailed description of the underlying mathematical components of
\code{aneris} as well as the procedural workflow. The results of applying the
automated harmonization mechanism on two example IAM scenarios, one with
emissions growth and another with emissions mitigation, is presented in Section
\ref{sec:results}. Finally, the general effectiveness and potential future
improvements on the automated methodology is discussed in Section
\ref{sec:future}.

\section{Methodology \& Implementation}\label{sec:meths}

@@

\subsection{\code{aneris} Workflow and Python Implementation}\label{sec:workflow}

We herein present \code{aneris}' conceptual workflow as well as specific details
of the Python implementation. The workflow is depicted in Figure
\ref{fig:workflow}, and the implementation is depicted in Figure
\ref{fig:software}.

\code{aneris} is comprised of a number of conceptual workflow and software
components shown graphically in Figures \ref{fig:workflow} and
\ref{fig:software}, respectively. Unharmonized model data and a run-control
configuration are read in via an Excel spreadsheet. Data is assumed to be in the
IAMC format, i.e., using \code{Model}, \code{Scenario}, \code{Region},
\code{Variable}, and \code{Unit} columns in addition to columns representing
each modeled time period.

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth]{implementation_schematic.pdf}
    \caption[]{
      \label{fig:software}
      foo
    }
  \end{center}
\end{figure}
